GSS Education and Environment

### 2023-04-05 outputs/paper/paper.qmd
Final commit for initial submission

clean_data_degree |>
  ggplot(aes(x = degree)) +
  geom_bar(fill = "turquoise4") +
  theme_minimal() +
  labs(x = "Highest Degree Obtained",
       y = "Number of Respondents",
       title = "Degree Obatined by Respondents")
```

@@

degree_and_donation |>
  ggplot(mapping = aes(x = degree, fill = grnmoney)) +
  geom_bar(position = "dodge2") +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "Highest Degree Obtained",
       y = "Number of Respondents",
       title = "Willingness and Donation Made by Degree")

>>>>

clean_data_degree |>
  ggplot(aes(x = degree)) +
  geom_bar(fill = "turquoise4") +
  theme_minimal() +
  labs(x = "Highest Degree Obtained",
       y = "Number of Respondents",
       title = "Degree Obtained by Respondents")
```

@@

degree_and_donation |>
  ggplot(mapping = aes(x = degree, fill = grnmoney)) +
  geom_bar(position = "dodge2") +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "Highest Degree Obtained",
       y = "Number of Respondents",
       title = "Donation Made to Environment by Degree")
